---
title: "Untitled"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
#__________________________________________________________________________________________________________________________________

# Investment case study

# Objective: Provide data-backed suggestions to Spark Funds, an assess management company, 
# to help them identify suitable investment targets based on best sectors, countries and investment types, 
# satisfying their 2 constraints:
# 1. Invest between 5M- 15M per round
# 2. Only invest in English-speaking countries, recognized by English being one of their official languages.

# Strategy: Spark only wants to invest where others are investing.

# Goals: To analyze global investment trends as provided by 3 data sets from crunchbase - companies, rounds2 and mapping.
#   1. Analyze investment types.
#   2. Analyze countries
#   3. Analyze sectors

# This R file holds the key to answering all questions pertaining to the 3 goals listed above.

#__________________________________________________________________________________________________________________________________

# Install packages needed if not already present

installed_packages <- installed.packages()[,1]
isFuzzyJoinInstalled <- "fuzzyjoin" %in% installed_packages
isTidyrInstalled <- "tidyr" %in% installed_packages
isDplyrInstalled <- "dplyr" %in% installed_packages
isStringrInstalled <- "stringr" %in% installed_packages

if(!isTidyrInstalled) {
  install.packages("tidyr")
}

if(!isDplyrInstalled) {
  install.packages("dplyr")
}

if(!isStringrInstalled) {
  install.packages("stringr")
}

if(!isFuzzyJoinInstalled) {
  install.packages("fuzzyjoin")
}

#__________________________________________________________________________________________________________________________________


# Load all necessary data manipulation packages.

library(tidyr)
library(dplyr)
library(stringr)
library(fuzzyjoin)

#__________________________________________________________________________________________________________________________________

# Stage 1: Data Understanding

#__________________________________________________________________________________________________________________________________

# Step 1: Load all the given data sets - companies, rounds2 and mapping

# Load companies data frame. Encode in UTF-8 to treat international characters in permalink, name correcty.
companies <- read.delim("companies.txt", stringsAsFactors = FALSE, check.names = FALSE)

#Load rounds2. Encode in UTF-8 to treat international characters in permalink, name correcty.
rounds2 <- read.csv("rounds2.csv", stringsAsFactors = FALSE, check.names = FALSE)

#Load mapping
mapping_cat_sec <- read.csv("mapping.csv", stringsAsFactors = FALSE, check.names = FALSE)

# Step 2: View the data sets to glean insights about their structure, relationships, cardinality, granularity and business-specific nuances
View(companies)
View(rounds2)
View(mapping_cat_sec)

# Basic understanding of the data sets
#   companies: 
#     -> Every row in this data frame corresponds to a unique company as identified by the key field permalink
#     -> Fields include: permalink, name, homepage_url, category_list, status, country_code, state_code, region, city, founded_at
#     -> Every company is mapped to multiple categories among which the first one is its primary category
#   rounds2:
#     -> Each row represents a funding received by a company in a specific investment type and round.
#     -> Fields include: company_permalink, funding_round_permalink, funding_round_type, funding_round_code, funded_at, raised_amount_usd
#     -> company_permalink is a reference field, referring to companies$permalink
#   mapping:
#     -> Given in wide format
#     -> Maps a company category to a sector.

#__________________________________________________________________________________________________________________________________

# Stage 2: Data cleaning and preparation

#__________________________________________________________________________________________________________________________________

#convert mapping data set from wide to long format
mapping <- gather(mapping_cat_sec,sector,value,`Automotive & Sports`:`Social, Finance, Analytics, Advertising`)
mapping <- mapping[!(mapping$value == 0),]
mapping <- mapping[, -3]

# The key field permalink may contain duplicates due to case mismatch.
# Add a new key field by converting permalink to uppercase.

#companies
company_mutated <- mutate(companies, upper_permalink = str_to_upper(permalink))

# In rounds2, the reference key field permalink may contain duplicates due to case mismatch.
# Add a new key field by converting company_permalink to uppercase.

rounds2_mutated <- mutate(rounds2, upper_permalink = str_to_upper(company_permalink))

# Merge companies and rounds2 data sets

# Creating master_frame
master_frame <- merge(x = rounds2_mutated, y = company_mutated, by = "upper_permalink", all.x = T)
#number of records in master_frame is 114949

# Separate out primary category from category list. 
# Ignore warnings.
# Warnings appear since the number of categories listed in the field "category_list"
# is variable, but we are interested in only the first one.

master_frame <- separate(master_frame, category_list, into=c("primary_cat"),sep="\\|",remove=F)
View(master_frame)
# master_frame contains 114949 records now also. 


#__________________________________________________________________________________________________________________________________

# Stage 3: Data analysis

#__________________________________________________________________________________________________________________________________

# Table -1.1


# 1. How many unique companies are present in rounds2?
nrow(distinct(rounds2_mutated, upper_permalink))

# 2. How many unique companies are present in the companies file?
nrow(distinct(company_mutated, upper_permalink))

# 3. In the companies data frame, which column can be used as the unique key for each company? Write the name of the column.
nrow(distinct(companies, permalink)) == nrow(companies)

# 4. Are there any companies in the rounds2 file which are not present in companies ? Answer Y/N.
length(setdiff(rounds2_mutated$upper_permalink, company_mutated$upper_permalink))

# 5. Merge the two data frames so that all variables (columns) in the companies frame are added to the rounds2 data frame.
# Name the merged frame master_frame.How many observations are present in master_frame ?
nrow(master_frame)


#__________________________________________________________________________________________________________________________________

# Table 2-1

#__________________________________________________________________________________________________________________________________

# Q 1-4
# Find the mean of raised amount (investment) for each funding type
#Average funding amount of venture type
#Average funding amount of angel type
#Average funding amount of seed type
#Average funding amount of private equity type

funding_type_mean <- summarise(group_by(master_frame,funding_round_type), avg_amount_raised = mean(raised_amount_usd, na.rm=T))
View(funding_type_mean)


# Based on the condition that we need to look at only angel, seed, private_equity and venture funding types,
# and that per round investment can only be between 5M and 15M, store the best suitable funding type in chosen_funding_type.

chosen_funding_type <- filter(funding_type_mean, funding_round_type %in% c("angel", "seed", "private_equity", "venture") & between(avg_amount_raised, 5000000, 15000000))
chosen_funding_type <- as.character(arrange(chosen_funding_type, desc(avg_amount_raised))[1, "funding_round_type"])
chosen_funding_type


#__________________________________________________________________________________________________________________________________

#Table 3-1

#__________________________________________________________________________________________________________________________________

# Spark Funds wants to see the top nine countries which have received the highest total funding 
# (across ALL sectors for the chosen investment type)

master_frame <- filter(master_frame, funding_round_type == chosen_funding_type)
View(master_frame)



# For the chosen investment type, make a data frame named top9 with the top nine countries 
# (based on the total investment amount each country has received)
raised_amounts_by_countries <- summarise(group_by(master_frame, country_code), raised_amount = sum(raised_amount_usd,na.rm = T))

top9 <- head(arrange(raised_amounts_by_countries, desc(raised_amount)), 9)
View(top9)

# Identify Top 3 English speaking countries

# To do this, we have to first map country_codes (distinct countrycodes in companies$country_code) to "English_speaking"
# Mapped "English_Speaking" to country codes by looking up country codes against 
# http://www.emmir.org/fileadmin/user_upload/admission/Countries_where_English_is_an_official_language.pdf
# Named the file as countrycode.csv with 2 fields - country_code and English_Speaking 
countrycode <- read.csv("countrycode.csv", stringsAsFactors = FALSE)
View(countrycode)

# Out of the top9 countries as stored in the data frame top9, filter only the top 3 English speaking countries
top3 <- merge(top9, countrycode, by = "country_code")
top3 <- head(arrange(filter(top3, English_speaking == 1), desc(raised_amount)), 3)$country_code



View(top3)

# Found that USA, GBR and IND are the top 3 English-speaking countries with highest investments in Venture funding type.

#__________________________________________________________________________________________________________________________________

# Table 4-1

#__________________________________________________________________________________________________________________________________


# Mapping sector to primary category an merging with the master frame
# Performing an inner join here. Ignoring primary category entries which do not have a sector mapping.
# If the primary category has no sector mapping, those data rows cannot be included in sector analysis.
# Also, mapping$category_list has some entries with incorrectly spelt categories, where the string "0"
# has replaced "na"s. Hence applying fuzzy_inner_join to use a custom matching function which
# maps the strings accurately.

category_matching_function <- function(master_frame_col, mapping_col) {
  correctedCol <- sub("0", "na", mapping_col )
  ret = (mapping_col == master_frame_col) |
          (str_to_upper(correctedCol) == str_to_upper(master_frame_col))
  ret
}

main_sector <- master_frame %>% fuzzy_inner_join(mapping, by = c(primary_cat = "category_list"), category_matching_function) 

# Only 8 sectors are considered. Removing Blanks
main_sector <- filter(main_sector, sector != "Blanks")
  

# Answer the following questions for USA, GBR and IND, given the constraint that Spark only wants to
# invest 5M to 15M per round, and only in venture funding type

#Total number of Investments (count)
#Total amount of investment (USD)
#Top Sector name (no. of investment-wise)
#Second Sector name (no. of investment-wise)
#Third Sector name (no. of investment-wise)
#Number of investments in top sector (3)
#Number of investments in second sector (4)
#Number of investments in third sector (5)
#For point 3 (top sector count-wise), which company received the highest investment?
#For point 4 (second best sector count-wise), which company received the highest investment?

# Create data frames D1, D2, D3
D1_interm_c1 <- filter(main_sector, country_code == top3[1] & raised_amount_usd >= 5000000 & raised_amount_usd <= 15000000)
D1 <- group_by(D1_interm_c1, sector) %>% summarise(count_inv = length(permalink), total_inv = sum(raised_amount_usd, na.rm=T))
D1 <- arrange(D1, desc(count_inv))
View(D1)


D2_interm_c2 <- filter(main_sector, country_code == top3[2] & raised_amount_usd >= 5000000 & raised_amount_usd <= 15000000)
D2 <- group_by(D2_interm_c2, sector) %>% summarise(count_inv = length(permalink), total_inv = sum(raised_amount_usd,na.rm = T))
D2 <- arrange(D2, desc(count_inv))
View(D2)

D3_interm_c3 <- filter(main_sector, country_code == top3[3] & raised_amount_usd >= 5000000 & raised_amount_usd <= 15000000)
D3 <- group_by(D3_interm_c3, sector) %>% summarise(count_inv = length(permalink), total_inv = sum(raised_amount_usd, na.rm = T))
D3 <- arrange(D3, desc(count_inv))
View(D3)


# To answer questions 1 and 2, for the 3 countries C1,C2 and C3 as found in top3
summarise(D1, cnt = sum(count_inv), tot = sum(total_inv))
summarise(D2, cnt = sum(count_inv), tot = sum(total_inv))
summarise(D3, cnt = sum(count_inv), tot = sum(total_inv))

#To answer questions 9 and 10, for the 3 countries - C1, C2, C3
# For C1, in the top sector, the best company 
arrange(summarise(group_by(filter(D1_interm_c1,sector == D1$sector[1]), upper_permalink), tot = sum(raised_amount_usd, na.rm=T), nm = unique(name)), desc(tot))$nm[1]

# For C1, in 2nd top sector, the best company
arrange(summarise(group_by(filter(D1_interm_c1,sector == D1$sector[2]), upper_permalink), tot = sum(raised_amount_usd, na.rm=T), nm = unique(name)), desc(tot))$nm[1]

# For C2, in the top sector, the best company 
arrange(summarise(group_by(filter(D2_interm_c2,sector == D2$sector[1]), upper_permalink), tot = sum(raised_amount_usd, na.rm=T), nm = unique(name)), desc(tot))$nm[1]

# For C2, in 2nd top sector, the best company
arrange(summarise(group_by(filter(D2_interm_c2,sector == D2$sector[2]), upper_permalink), tot = sum(raised_amount_usd, na.rm=T), nm = unique(name)), desc(tot))$nm[1]

# For C3, in the top sector, the best company 
arrange(summarise(group_by(filter(D3_interm_c3,sector == D3$sector[1]), upper_permalink), tot = sum(raised_amount_usd, na.rm=T), nm = unique(name)), desc(tot))$nm[1]

# For C3, in 2nd top sector, the best company
arrange(summarise(group_by(filter(D3_interm_c3,sector == D3$sector[2]), upper_permalink), tot = sum(raised_amount_usd, na.rm=T), nm = unique(name)), desc(tot))$nm[1]


# Denormalizing D1 to include all fields of main_sector df as per instructions
D1 <- merge(D1_interm_c1, D1, by = "sector")
D2 <- merge(D2_interm_c2, D2, by = "sector")
D3 <- merge(D3_interm_c3, D3, by = "sector")

```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
